
# Intro to Data Science - HW 2

##### Copyright 2022, Jeffrey Stanton, Jeffrey Saltz, and Jasmina Tacheva

```{r}
# Enter your name here: 
```

### Attribution statement: (choose only one and delete the rest)

```{r}
# 1. I did this homework by myself, with help from the book and the professor.
# 2. I did this homework with help from the book and the professor and these Internet sources:
# 3. I did this homework with help from <Name of another student> but did not cut and paste any code.
```

### Reminders of things to practice from last week: 
Assignment arrow:  		<- <br>
The combine command: 	c( ) <br>
Descriptive statistics: 	mean( ) sum( ) max( ) <br>
Arithmetic operators:		+ - * /<br>
Boolean operators:		>    <    >=    <=   ==   !=  <br>

**This Week:** Explore the **quakes** dataset (which is included in R). 


<br>
<br>

**Step 0:** Prepare the data <br>
A. Copy the **quakes** dataset into a new dataframe (call it **myQuakes**), so that if you need to start over, you can do so easily (by copying **quakes** into **myQuakes** again). Summarize the variables in **myQuakes** using an R command. Also, explore the structure of the dataframe - using another R command. In a brief comment, describe what this dataset is about based on your analysis of the variables in it. 

```{r}

```

**Step 1:** Explore the earthquake magnitude variable called **mag**  <br>

A.	What is the average magnitude? Use mean() or summary():

```{r}

```

B.	What is the magnitude of the smallest earthquake? Use min() or summary() and save the result in a variable called **minQuake**:

```{r}

```

C.	What is the magnitude of the largest earthquake? Use max() or summary() and save the result in a variable called **maxQuake**:

```{r}

```

D.	Output the **fourth row** of the dataframe:

```{r}

```

E. Create a new dataframe, with only the rows where the **magnitude is greater than 4**. How many rows are in that dataframe (report this number using code, do not count by looking at the output):

```{r}

```

F.	Using the **arrange()** function, create a **sorted dataframe** based on magnitude and store it in **quakeSorted1**. Explain how this function works.

```{r}

```

G. Now create a second sorted dataframe called **quakeSorted2** using the **order()** function. Explain in a comment how the function works.

```{r}

```

H. Print the top rows of each of the sorted dataframes using the **head()** function and explain in a comment what you see - did the two sorting functions produce a similar result?

```{r}

```

```{r}

```

I.	What are the latitude and longitude of the quake reported by the largest number of stations?  

```{r}

```

J.	What are the latitude and longitude of the quake with the smallest magnitude?  

```{r}

```

**Step 3:** Using conditional if statements <br>

A.	 Test if **maxQuake** is greater than 6 (output  yes  or  no ) <br>
**Hint:** Try modifying the following code in R: 

```{r}
if  (100 < 150) "100 is less than 150" else "100 is greater than 150"
```

B.	 Following the same logic, test if **minQuake** is less than 3 (output  yes  or  no ):

```{r}

```

