
# Intro to Data Science - HW 4

##### Copyright 2022, Jeffrey Stanton, Jeffrey Saltz, and Jasmina Tacheva

```{r}
# Enter your name here: 
```

### Attribution statement: (choose only one and delete the rest)

```{r}
# 1. I did this homework by myself, with help from the book and the professor.
# 2. I did this homework with help from the book and the professor and these Internet sources:
# 3. I did this homework with help from <Name of another student> but did not cut and paste any code.
```

**(Chapter 6 of Introduction to Data Science)** <br>

Reminders of things to practice from previous weeks: <br>
Descriptive statistics: 	mean( )  max( ) min( )<br>
Sequence operator:		: (For example, 1:4 is shorthand for 1, 2, 3, 4)<br>
Create a function:		myFunc <- function(myArg) { }<br>
?command:			Ask R for help with a command<br>

**This module:** **Sampling** is a process of **drawing elements from a larger set**. In data science, when analysts work with data, they often work with a sample of the data, rather than all of the data (which we call the **population**), because of the expense of obtaining all of the data. <br>

One must be careful, however, because **statistics from a sample rarely match the characteristics of the population**. The **goal of this homework** is to **sample from a data set several times and explore the meaning of the results**. Before you get started make sure to read Chapter 6 of *An Introduction to Data Science*. Don t forget your comments!

## Part 1: Write a function to compute statistics for a vector of numeric values

A.	Create a new function which takes a numeric vector as its input argument and returns a dataframe of statistics about that vector as the output. As a start, the dataframe should have the **min**, **mean**, and **max** of the vector. The function should be called **statsCalc**:

```{r}

```

B.	Test your function by calling it with the numbers **one through ten**:

```{r}
statsCalc(1:10)
```

C.	Enhance the statsCalc() function to add the **median** and **standard deviation** to the returned dataframe.

```{r}

```

D.	Retest your enhanced function by calling it with the numbers **one through ten**:

Note that the code below has an error, so just running the code will not work. Fix the code and then run test function.

```{r}
statsCalculator(1:10)
```

## Part 2: Sample repeatedly from the New York State COVID Testing Dataset from HW 3

A.	Load the dataset from the following URL, using read_csv: https://data-science-intro.s3.us-east-2.amazonaws.com/NYS_COVID_Testing.csv

```{r}
 
```

B. Use **head(testDF)** and **tail(testDF)** to show the data. Add a comment that describes what each variable in the data set contains. <br>

```{r}

```

C.	Sample ten observations from **testDF$TotalTests**.

```{r}

```

D.	Call your statsCalc( ) function with a new sample of ten observations from **testDF$TotalTests**, where the sampling is done inside the **statsCalc** function call. 

```{r}

```

E. Now use the **mean()** function, with another sample done inside the mean function. Is the mean returned from the **statsCalc** function the same as the mean returned from the mean function on this sample? Why or why not? Explain.

```{r}

```

F.	Use the **replicate( )** function to repeat your sampling of **testDF$TotalTests** twenty times, with each sample calling **mean()** on ten observations. The first argument to **replicate( )** is the number of repeats you want. The second argument is the little chunk of code you want repeated.

```{r}

```

G.	Write a comment describing why every replication produces a different result.

```{r}

```

H.	Rerun your replication, this time doing 20 replications and storing the output of **replicate()** in a variable called **values**.

```{r}

```

I.	 Generate a **histogram** of the means stored in **values**. 

```{r}

```

J.	Repeat the replicated sampling, but this time, raise your replications to **1000**. 

```{r}

```

K. Compare the two histograms - why are they different? Explain in a comment.

```{r}

```

