
# Intro to Data Science HW 8
##### Copyright 2022, Jeffrey Stanton, Jeffrey Saltz, and Jasmina Tacheva

```{r}
# Enter your name here: 
```

### Attribution statement: (choose only one and delete the rest)

```{r}
# 1. I did this homework by myself, with help from the book and the professor.
# 2. I did this homework with help from the book and the professor and these Internet sources:
# 3. I did this homework with help from <Name of another student> but did not cut and paste any code.
```

The chapter on **linear models** ( Lining Up Our Models ) introduces **linear predictive modeling** using the tool known as **multiple regression**. The term  multiple regression  has an odd history, dating back to an early scientific observation of a phenomenon called ** regression to the mean. ** These days, multiple regression is just an interesting name for using **linear modeling** to assess the **connection between one or more predictor variables and an outcome variable**. 


<br>In this exercise, you will **predict food insecurity from three predictors**.

A.	We will be using the **Food Insecurity** data set from HW7. Copy it from this URL: 

https://data-science-intro.s3.us-east-2.amazonaws.com/FoodInsecurity.csv

 into a dataframe called **df** and use the appropriate functions to **summarize the data**. 

```{r}

```

B.	In the analysis that follows, **LAPOP1_10** will be considered as the **outcome variable**, and **Pop2010**, **AveragePovertyRate**, and **MedianFamilyIncome** as the **predictors**. Add a comment to briefly explain the outcome variable (take a look at HW 7 if needed).

```{r}

```

C.	Inspect the outcome and predictor variables  are there any missing values? Show the code you used to check for that.

```{r}

```

D. What does it mean when the output of the is.na() function is empty? Explain in a comment. Are all predictors coded as numerical variables? Show your code to check for that and if they are not - find a way to fix this issue, re-check for missing values, and implement a strategy to deal with them if present (Hint - **imputeTS** might help).

```{r}

```

E.	Create **3 bivariate scatterplots (X-Y) plots** (using ggplot), for each of the predictors with the outcome. **Hint:** In each case, put **LAPOP1_10 on the Y-axis**, and a **predictor on the X-axis**. Add a comment to each, describing the plot and explaining whether there appears to be a **linear relationship** between the outcome variable and the respective predictor.

```{r}

```

F.	Next, create a **simple regression model** predicting **LAPOP1_10 based on Pop2010**, using the **lm( )** command. In a comment, report the **coefficient** (aka **slope** or **beta weight**) of **Pop2010** in the regression output and, **if it is statistically significant**, **interpret it** with respect to **LAPOP1_10**. Report the **adjusted R-squared** of the model and try to explain what it means. 

```{r}

```

G.	Create a **multiple regression model** predicting **LAPOP1_10** based on **Pop2010**, **AveragePovertyRate**, and **MedianFamilyIncome**.<br> **Make sure to include all three predictors in one model   NOT three different models each with one predictor.**

```{r}

```

H.	Report the **adjusted R-Squared** in a comment.   How does it compare to the adjusted R-squared from Step F? Is this better or worse? Which of the predictors are **statistically significant** in the model? In a comment, report the coefficient of each predictor that is statistically significant. Do not report the coefficients for predictors that are not significant.

```{r}

```

I.	Create a one-row data frame like this: 

```{r}
predDF <- data.frame(Pop2010=100000, AveragePovertyRate=20, MedianFamilyIncome=65000)
```

 and use it with the **predict( )** function to predict the **expected value of LAPOP1_10**:

```{r}

```
 Describe the accuracy of the prediction.  

```{r}

```

J.	Create an additional **multiple regression model**, with **AveragePovertyRate** as the **outcome variable**, and the other **3 variables** as the **predictors**. 

Review the quality of the model by commenting on its **adjusted R-Squared**.  

```{r}

```

