
# Intro to Data Science - Lab 3
##### Copyright 2022, Jeffrey Stanton and Jeffrey Saltz   Please do not post online.

## Week 3 - Using Descriptive Statistics & Writing Functions

```{r}
# Enter your name here: 
```

### Please include nice comments. <br>
### Instructions: 
Run the necessary code on your own instance of R-Studio.Save the
code: It will be useful on your homework!

### Attribution statement: (choose only one and delete the rest)

```{r}
# 1. I did this lab assignment by myself, with help from the book and the professor.
# 2. I did this lab assignment with help from the book and the professor and these Internet sources:
# 3. I did this lab assignment with help from <Name of another student> but did not cut and paste any code.
```


1. Get	an	explanation	of	the	contents	of	the	**state.x77**	data	set:<br>	`help("state.x77")`

```{r}

```

2. Create	a	dataframe	from	the	built-in **state.x77**	data	set,	store	in	a	variable	named ** dfStates77 **

```{r}

```

3. Summarize	the	variables	in	your	**dfStates77**	data	set	-	using	the	**summary()**
function

```{r}

```

4. Calculate	the	total	population	of	the	U.S. by	adding	together	the	populations	of
each	of	the	individual	states	in	**dfStates77**.			Store	the	result	in	a	new	variable
called	**totalPop77**.

```{r}

```

5. Use	R	code	to	read	a	CSV	data	file	directly	from	the	web.	Store	the	dataset	into	a
new	dataframe,	called	dfStates17.	The	URL	is:
"https://intro-datascience.s3.us-east-2.amazonaws.com/statesNew.csv" <br>
Note:	Use	the	function	**read_csv(	)**	to	read	in	the	data.
You	will	need	to	run	`library(tidyverse)`	before	you	can	run **read_csv(	)**.		If	that	generates	an	error,	then	you	first	need	to	do <br>
`install.packages("tidyverse")`

```{r}

```

6. Summarize	the	variables	in	your	new	data	set,	using	the	**summary()** command.

```{r}

```

7. The	data	you	now	have	stored	in	**dfStates17** were	collected	in	2017.	As	such,
about	40	years	passed	between	the	two	data	collections.	Calculate	the	total	2017
population	of	the	U.S.	in	**dfStates17**	by	adding	together	the	populations	of	each	of
the	individual	states.	Store	the	result	in	a	new	variable	called	**totalPop17**.

```{r}

```

8. Create	and	interpret	a	ratio	of	**totalPop77** to	**totalPop17**.	Check	to	ensure	that	the result	makes	sense!<br>

Create	a	function	that,	given	population	and	area,	calculates	population	density	by	
dividing	a	population	value	by	an	area	value.	Here	is	the	core	of	the	function:	<br>


```
popDensity <- function (pop, area) {
 # Add your code below here:
 # Next, divide pop by area and store the result in a
 # variable called popDens
 return(popDens) # This provides the function s output
}
```




```{r}

```

9. After	you	finish	your	function,	make	sure	to	run	all	of	the	lines	of	code	in	it	so
that	the	function	becomes	known	to	R.

10. Make	a	fresh	copy	of	**state.x77**	into	**dfStates77**

```{r}

```

11. Store	the	population	vector	in	a	variable	called	**tempPop**.	Adjust	the	**tempPop**	as
needed	(based	on	your	analysis	above)

```{r}

```

12. Store	the	area	vector	in	a	variable,	called	**tempArea**

```{r}

```

13. Now	use	**tempPop**	and	tempArea	to	call	your	function:<br>
`popDensity(tempPop,	tempArea)`

```{r}

```

14. Store	the	results	from		the	previous	task	in	a	column	of	the	**dfStates77**
dataframe,	called	**popDensity**.

```{r}

```

15. Use	**which.max(	)**	and	**which.min(	)**	to	reveal	which	is	the	most	densely
populated	and	which	is	the	least	densely	populated	state.	Make	sure	that	you
understand	the	number	that	is	revealed	as	well	as	the	name	of	the	state.

```{r}

```

16. Using	tidyverse,	sort	the	dataframe	using	the	**popDensity**	attribute,	then	using
the	**slice()**	function,	show	the	first	row	in	the	sorted	database.

```{r}

```

17. How	was	the	dataframe	sorted	(was	the	minimum	first	or	the	maximum)? Explain in a comment.

```{r}

```

