

# Intro to Data Science - Lab 4
##### Copyright 2022, Jeffrey Stanton and Jeffrey Saltz   Please do not post online.

## Week 4 - Sampling

```{r}
# Enter your name here: 
```

### Please include nice comments. <br>
### Instructions: 
Run the necessary code on your own instance of R-Studio.

### Attribution statement: (choose only one and delete the rest)

```{r}
# 1. I did this lab assignment by myself, with help from the book and the professor.
# 2. I did this lab assignment with help from the book and the professor and these Internet sources:
# 3. I did this lab assignment with help from <Name of another student> but did not cut and paste any code.
```

A key focus of this week is how to make inferences about populations based on samples. The
essential logic lies in comparing a single instance of a statistic such as a sample mean to a
distribution of such values. The comparison can lead to one of two conclusions   the sample
statistic is either extreme or not extreme. But what are the thresholds for making this kind of
judgment call (i.e., whether a value is extreme or not)? This activity explores that question.<br><br>
**The problem is this:** You receive a sample containing the ages of 30 students. You are wondering
whether this sample is a group of **undergraduates** (mean age = 20 years) or **graduates** (mean age
= 25 years).<br><br> To answer this question, you must compare the mean of the sample you receive to a
distribution of means from the population. The following fragment of R code begins the solution:<br><br>


```
set.seed(2)
sampleSize <- 30
studentPop <- rnorm(20000,mean=20,sd=3)
undergrads <- sample(studentPop,size=sampleSize,replace=TRUE)
grads <- rnorm(sampleSize,mean=25,sd=3)
if (runif(1)>0.5) { testSample <- grads } else { testSample <- undergrads }
mean(testSample)
```



After you run this code, the variable ** testSample ** will contain either a sample of undergrads or a
sample of grads. The line before last  flips a coin  by generating one value from a **uniform
distribution** (by default the distribution covers 0 to 1) and comparing it to 0.5. The question you
must answer with additional code is: Which is it, grad or undergrad?<br><br>
Here are the steps that will help you finish the job:

1. Copy	the	code	above and annotate it	with	line-by-line	commentary.	In	other	words,	you	must	explain what	
each	of	the	seven	lines	of	code	above	actually	do!	You	will	have	to	lookup	the	meaning	of some	
commands.

```{r}

```

2. Generate 10	samples	from	the	** undergrads **	dataset.

```{r}

```

3. Generate	10	new	samples	and	take	the	mean	of	that	sample

```{r}

```

4. Repeat	this	process	3	times	(i.e.,	generate	a	sample	and	take	the	mean	3	times,	using	the
replicate	function).

```{r}

```

5. Generate	a	list	of	sample	means	from	the	population	called	** undergrads **
How	many	sample	means	should	you	generate?	Really,	you	can	create	any	number	that	you
want  	hundreds,	thousands,	whatever	 	but	I	suggest	for	ease	of	inspection	that	you generate just	100	means.	That	is	a	pretty	small	number,	but	it	makes	it	easy	to	think	about percentiles	
and	ranks.

```{r}

```

6. Once	you	have	your	list	of	sample	means	generated	from	**undergrads**,	the	trick	is	to compare	**mean(testSample)**	to	that	list	of	sample	means	and	see	where	it	falls.
Is	it	in	the	middle	of	the	pack?	Far	out	toward	one	end?	<br>Here	is	one	hint	that	will	help	you: In	chapter	7,	the	**quantile()**	command	is	used	to	generate	percentiles	based	on	thresholds of	2.5%	and	97.5%.	Those	are	the	thresholds	we	want,	and	the	**quantile()**	command	will	help	you create	them.	

```{r}

```

7. Your	code	should	have a	**print()**	statement	that	should	say	either,	 Sample	mean	is extreme, 	or,	
 Sample	mean	is	not	extreme. 

```{r}

```

8. Add	a	comment	stating	if	you	think	the	**testSample**	are	undergrad	students.	Explain	why	or why not.

```{r}

```

9. Repeat	the	same	analysis	to	see	if	the	**testSample**	are	grad	students.

```{r}

```

