
# Intro to Data Science - Lab 5
##### Copyright 2022, Jeffrey Stanton and Jeffrey Saltz   Please do not post online.

## Week 5 - Obtaining	and	Using	Data	from	a	JSON	API	

```{r}
# Enter your name here: 
```

### Please include nice comments. <br>
### Instructions: 
Run the necessary code on your own instance of R-Studio.

### Attribution statement: (choose only one and delete the rest)

```{r}
# 1. I did this lab assignment by myself, with help from the book and the professor.
# 2. I did this lab assignment with help from the book and the professor and these Internet sources:
# 3. I did this lab assignment with help from <Name of another student> but did not cut and paste any code.
```

**JSON	(JavaScript	Object	Notation)**	provides	a	transparent,	user	friendly	
data	exchange	format	that	many	organizations	use	to	make	their	data	available	over	
the	web.	JSON	is	human	readable,	but	is	also	highly	structured,	and	its	support	for	
nested	data	structures	makes	it	highly	flexible.<br> <br>	Today	we	will	use	JSON	to	obtain	data	from	the	**NYC	CitiBike	project**.	The	CitiBike	project	provides	an	application	
programming	interface	(API)	that	members	of	the	public	can	access to	get	up-todate	information	on	the	status	of	more	than	800	bike	stations.	<br> <br>
You	may	need	to	install	the	**RCurl**	and	**jsonlite**	packages	to	get	the	code	to	work.	<br> <br>



```
station_link <- 'https://gbfs.citibikenyc.com/gbfs/en/station_status.json'
apiOutput <- getURL(station_link)
apiData <- fromJSON(apiOutput)
stationStatus <- apiData$data$stations
cols <- c('num_bikes_disabled','num_docks_disabled', 'station_id',
 'num_ebikes_available', 'num_bikes_available', 'num_docks_available')
stationStatus = stationStatus[,cols]
```



1. Explain	what	you	see	if	you	type	in	the	**station_link**	URL	into	a	browser	(in	a
comment,	write	what	you	see)

```{r}

```

2. Paste the code from above here and provide	a	comment	explaining	each	line	of	code.

```{r}

```

3. Use	**str(	)**	to	find	out	the	structure	of	**apiOutput**	and	**apiData**.	Report (via	a
comment) what	you	found	and	explain	the	difference	between	these	two	objects.

```{r}

```

4. The	**apiOutput**	object	can	also	be	examined	with	a	custom	function	from	the **jsonlite**	package	called	**prettify(	)**.	Run	this	command	and	explain what	you
found (in	a	comment).

```{r}

```

5. Explain	**stationStatus**	(what	type	of	object,	what	information	is	available).

```{r}

```

6. Generate	a	histogram	of	the	number	of	docks	available

```{r}

```

7. Generate	a	histogram	of	the	number	of	bikes	available

```{r}

```

8. How	many	stations	have	at	least	one	ebike?

```{r}

```

9. Explore	stations	with	at	least	one	ebike	by	create	a	new	dataframe,	that	only	has
stations	with	at	least	one	eBike.

```{r}

```

10. Calculate	the	mean	of	** num_docks_available **	for	this	new	dataframe.

```{r}

```

11. Calculate	the	mean	of	** num_docks_available **	for	for	the	full	** stationStatus **
dataframe.	In	a	comment,	explain	how	different	are	the	two	means?

```{r}

```

12. Create	a	new	attribute,	called	** stationSize **,	which	is	the	total	number	of	 slots 
available	for	a	bike	(that	might,	or	might	not,	have	a	bike	in	it	now).	Run	a
histogram	on	this	variable	and	review	the	distribution.

```{r}

```

13. Use the	**plot(	)**	command	to produce	an	X-Y	scatter	plot	with	the	number	of
occupied	docks	on	the	X-axis	and	the	number	of	available	bikes	on	the	Y-axis.
Explain	the	results	plot.

```{r}

```

