
# Intro to Data Science - Lab 7
##### Copyright 2022, Jeffrey Stanton and Jeffrey Saltz   Please do not post online.

## Week 7 - Using	ggplot	to	Build	 Complex	Data	Displays

```{r}
# Enter your name here: 
```

### Please include nice comments. <br>
### Instructions: 
Run the necessary code on your own instance of R-Studio.

### Attribution statement: (choose only one and delete the rest)

```{r}
# 1. I did this lab assignment by myself, with help from the book and the professor.
# 2. I did this lab assignment with help from the book and the professor and these Internet sources:
# 3. I did this lab assignment with help from <Name of another student> but did not cut and paste any code.
```

 Geology rocks but geography is where it's at. . .  (famous dad joke). In
a global economy, geography has an important influence on everything from
manufacturing to marketing to transportation. As a result, most data scientists will
have to work with map data at some point in their careers. <br><br>

An add-on to the **ggplot2** package, called **ggmap**, provides powerful tools for plotting and shading maps.<br><Br>
Make sure to install the **maps**, **mapproj**, and **ggmap** packages before running the following:



```
library(ggplot2); library(maps); library(ggmap); library(mapproj)
us <- map_data("state")
us$state_name <- tolower(us$region)
map <- ggplot(us, aes(map_id= state_name))
map <- map + aes(x=long, y=lat, group=group) +
geom_polygon(fill = "white", color = "black")
map <- map + expand_limits(x=us$long, y=us$lat)
map <- map + coord_map() + ggtitle("USA Map")
map
```



1. Paste the code below and add a comment for each line, explaining what that line of code does.

```{r}

```

2. The map you just created fills in the area of each state in white while outlining it with a thin black line. Use the **fill=** and **color=** commands inside the call to **geom_polygon( )** to reverse the color scheme.<br><br>
Now paste and run the following code:<br><br>


```
ny_counties <- map_data("county","new york")
ggplot(ny_counties) + aes(long,lat, group=group) + geom_polygon(fill
= "white", color = "black")
```


```{r}

```

3. Just as in step 2, the map you just created fills in the area of each county in black
while outlining it with a thin white lines. Use the **fill=** and **color=** commands
inside the call to **geom_polygon( )** to reverse the color scheme.

```{r}

```

4. Run `head(ny_counties)` to verify how the county outline data looks

```{r}

```

5. Make a copy of your code from step 3 and add the following subcommand to
your ggplot( ) call (don t forget to put a plus sign after the **geom_polygon( )** statement to tell R that you are continuing to build the command):<br><br>
`coord_map(projection = "mercator")` <br><br>
In what way is the map different from the previous map. Be prepared to explain
what a Mercator projection is. 

```{r}

```

6. Grab a copy of the nyData.csv data set from:
https://intro-datascience.s3.us-east-2.amazonaws.com/nyData.csv
<br><br>Read that data set into R with **read_csv()**. This will require you have installed
and libraried the **tidyverse** package. The next step assumes that you have named the
resulting data frame ** nyData. **

```{r}

```

7. Next, merge your **ny_counties** data from the first set of
questions with your new **nyData** data frame, with this code:<br><br>
`mergeNY <- merge(ny_counties,nyData,all.x=TRUE,by.x="subregion",by.y="county")`



```{r}

```

8. Run `head(mergeNY)` to verify how the merged data looks.

```{r}

```

9. Now drive the fill color inside each county by adding the **fill** aesthetic inside of
your **geom_polygon( )** subcommand (fill based on **pop2000**).

```{r}

```

10. Extra (not required):<br>
a. Read in the following JSON datasets:
'https://gbfs.citibikenyc.com/gbfs/en/station_information.json'
'https://gbfs.citibikenyc.com/gbfs/en/station_status.json'<br>
b. Merge the datasets, based on ** station_id **<br>
c. Clean the merged dataset to only include useful information<br>
For this work, you only need lat, lon and the number of bikes available
d. Create a stamen map using ** get_stamenmap() **<br>
Have the limits of the map be defined by the lat and lot of the stations<br>
e. Show the stations, as points on the map.<br>
f. Show the number of bikes available as a color

```{r}

```

